---
title: "My Awesome Report"
author: "Emmet Brickowski"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))
```


# My Awesome Report
## Section title
### Sub-section
#### Sub-sub section
##### Sub-sub-sub section

## Introduction

In this workshop, I learned **really cool** things! And I mean ***REALLY*** cool!

For example, we learned about **tidyverse**, using the *SAFI* dataset. The *SAFI*
dataset contains the following variables:

- village
  + Name of the village
- interview_date
- no_members
  + How many family members in a house
- years_liv
- respondent_wall_type
- rooms

<!-- this is a comment -->

write something important

This is ranking of my favourite variables:

1. rooms
2. no_members
3. years_liv

## Results

```{r table-1, echo=FALSE, message=FALSE}
interviews %>%
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>%
  knitr::kable(
    col.names = c("Village", "Member of Association", "Mean Number of Members"),
    caption = "Pretty table"
    )
```

<!-- data visualisation with ggplot2 -->

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items))
```






