---
title: "My Awesome Report"
author: "Emmet Brickowski"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))
```


# My Awesome Report
## Section title
### Sub-section
#### Sub-sub section
##### Sub-sub-sub section

## Introduction

In this workshop, I learned **really cool** things! And I mean ***REALLY*** cool!

For example, we learned about **tidyverse**, using the *SAFI* dataset. The *SAFI*
dataset contains the following variables:

- village
  + Name of the village
- interview_date
- no_members
  + How many family members in a house
- years_liv
- respondent_wall_type
- rooms

<!-- this is a comment -->

write something important

This is ranking of my favourite variables:

1. rooms
2. no_members
3. years_liv

## Results

```{r table-1, echo=FALSE, message=FALSE}
interviews %>%
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>%
  knitr::kable(
    col.names = c("Village", "Member of Association", "Mean Number of Members"),
    caption = "Pretty table"
    )
```

<!-- data visualisation with ggplot2 -->

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items)) + 
    geom_point(alpha = 0.3) # code for a scatter plot
```

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items, colour = village)) +
    geom_jitter(
      #colour = "blue", # add colour to all points
      alpha = 0.3, 
      width = 0.2, # random noise on x-axis
      height = 0.2 # random noise on y-axis
    )
```

```{r}
interviews_plotting %>%
  ggplot(aes(x = no_membrs, y = number_items, colour = village)) +
    geom_count()
```

```{r rooms-village-scatter}
interviews_plotting %>% 
  ggplot(aes(x = rooms, y = village, colour = respondent_wall_type)) + 
  geom_point()
```

<!-- boxplots might be better...-->

```{r}
respondent_rooms_plot <- interviews_plotting %>%
  ggplot(aes(y = rooms, x = village, colour = respondent_wall_type))

respondent_rooms_plot +
  geom_boxplot()
```

```{r}
interviews_plotting %>% 
  ggplot(aes(x = respondent_wall_type, y = rooms)) +
    geom_violin() +
    geom_jitter(
      alpha = 0.3,
      colour = "tomato",
      width = 0.2,
      height = 0.2
    )
```

<!-- Bar plots -->

```{r}
interviews_plotting %>%
  ggplot(aes(x = respondent_wall_type)) +
    geom_bar(aes(fill = village)) # fill colours the bars in the plot
```

```{r}
interviews_plotting %>%
  ggplot(aes(x = respondent_wall_type)) +
    geom_bar(aes(fill = village), position = "dodge") # fill colours the bars in the plot
```

<!-- relative contributions of the variables instead of absolute-->

```{r}
percent_wall_type <- interviews_plotting %>%
  filter(respondent_wall_type != "cement") %>% 
  count(village, respondent_wall_type) %>%
  group_by(village) %>% 
  mutate(percent = (n / sum(n)) * 100) %>% 
  ungroup()
```

`geom_bar` only allows x or y (not both).
`geom_col` allows both.

```{r}
percent_wall_type %>% 
  ggplot(aes(x = respondent_wall_type, y = percent, fill = respondent_wall_type)) +
    #geom_bar(position = "dodge", stat = "identity") # solution 1
    geom_col(position = "dodge") + # solution 2
    labs(
      title = "Proportion of wall type by village",
      x = "Wall type",
      y = "Percent"
      ) +
    facet_wrap(~ village) +
    theme_bw() +
    theme(panel.grid.major.x = element_blank(),
          axis.text.x = element_text(angle = 45)) +
    scale_fill_viridis_d()
```







